---
title: "Draft_3_Soyan_loading_texts"
author: "Rossina Soyan"
date: "11/24/2021"
output:
  github_document: 
    toc: TRUE
---
# How to load a corpus of texts?

```{r setup}
##Set knitr options (show both code and output, show output w/o leading #, make figures smaller, hold figures until after chunk)
knitr::opts_chunk$set(echo=TRUE, include=TRUE, comment=NA, fig.height=3, fig.width=4.2, fig.show="hold")
Sys.setlocale("LC_CTYPE", "Russian") #to make sure my text is not gibberish, readable
```

## Steps for completing this final project

I will write down the steps from the final goal back to the beginning

1.Conduct a cluster analysis and determine which lexical complexity measures are typical for each proficiency level in WPT

2. Measure lexical complexity measures in all texts. Some people have written up to three texts. It means I need to combine and average their scores and then input it into the cluster analysis

3. Upload the corpus, create a dataframe with texts and names. 




## What I need to install to run the codes?

```{r}
library(tidyverse)
#install.packages('quanteda') to work with a corpus
library(quanteda)
#install.packages("htmlwidgets") to work with strings and regular expressions
library(htmlwidgets)
# install.packages('tidytext') to be able to perform tokenization
library(tidytext)
#install.packages('corpus')
library(corpus) #To split the text into sentences
#install.packages('spacyr')
library(spacyr) #to be able to count the T-units

```

## Loading a corpus

```{r}
#From https://www.youtube.com/watch?v=pFinlXYLZ-A
folderPre0 <- "C:/Users/Rossina/Documents/CMU_student/3_Fall_2021/Statistics_at_Pitt/2019_Standardized/2019_PreTest_ST/Pre_test_Prompt0_Planning_dinner_party_ST"
filelistPre0_orig <- list.files(path = folderPre0, pattern = ".*.txt")
filelistPre0_orig
filelistPre0 <- paste(folderPre0, "/", filelistPre0_orig, sep = "")
filelistPre0
filelistPre0texts <- lapply(filelistPre0, FUN = readLines, encoding = "UTF-8", warn = FALSE)
textsPre0 <- lapply(filelistPre0texts, FUN = paste, collapse = " ") %>% 
  str_remove_all("unclear")
textsPre0
```

## Cleaning the corpus

Next, I want to get rid of the word "unclear" and I want to create a tibble with the names of texts.

```{r}
#Another option proposed by Dan is above
#stopwords = "unclear"
#removeWords <- function(str, stopwords) {
 # x <- unlist(strsplit(str, " "))
  #paste(x[!x %in% stopwords], collapse = " ")
#}

#textsPre0 <- lapply(textsPre0, FUN = removeWords, stopwords) #Success!!!
#textsPre0
class(textsPre0) #The class is list. How do I move on from here?


corpus_df <- tibble(text = unlist(textsPre0), Student = 1:8)
corpus_df #Success. 

```
## How to load all texts and WPT ratings?

I know how to load a number of texts, but I need to also indicate the author and their rating. I guess it will happen a little bit later in the process.

## Calculating and adding lexical complexity measures to the corpus_df

```{r}
# How do I create a tidy text? Let's see
corpus_df_tidy <- corpus_df %>% 
  mutate(text = gsub(x = text, pattern = "\\-\\s", replacement = "")) %>% #what to do is lonely dashes? 
  unnest_tokens(word, text, token = "regex", pattern = "[\\s,\\.\\?!\\(\\)\\:\";]") #let me check if words look like real words in all these 8 texts
corpus_df_tidy %>% 
  filter(str_detect(word, "-")) #Success! 
```

### Lexical density

```{r}
RusConjCoord2 <- readLines("additional_documents/Russian_conjunctions_COORD.txt", encoding = "UTF-8", warn = FALSE) %>% 
  str_remove_all("<.+>") 
RusPrep2 <- readLines("additional_documents/Russian_prepositions.txt", encoding = "UTF-8", warn = FALSE) %>% 
  str_remove_all("<.+>") 
RusConjSubord2 <- readLines("additional_documents/Russian_conjunctions_SUBORD.txt", encoding = "UTF-8", warn = FALSE) %>% 
  str_remove_all("<.+>")
RusInter2 <- readLines("additional_documents/Russian_interjections.txt", encoding = "UTF-8", warn = FALSE) %>%
  str_remove_all("<.+>")
RusPrtcl2 <- readLines("additional_documents/Russian_particles.txt", encoding = "UTF-8", warn = FALSE) %>% 
  str_remove_all("<.+>") 
AllnonLEX <- c(RusConjCoord2, RusPrep2, RusConjSubord2, RusInter2, RusPrtcl2) 
AllnonLEX_df <- tibble(word = AllnonLEX) #This column name should be the same for using the anti-join()
AllnonLEX_df #Success! 
```

I am not sure what is next. Let's try writing the function for lexical density

```{r}
lexical_words <- function(x){
 lexical_words <- anti_join(x, AllnonLEX_df, by = "word")
   return(lexical_words)
}

#lexical_words(corpus_df_tidy$word) Spits out TRUE and FALSE, not what I want

#lexical_density <- function(x){
 # density <- nrow(lexical_words(x))/nrow(x)
  #return(density)
#}

#corpus_df_tidy %>% 
 # group_by(names) %>% 
  #summarize(lexical_density = lexical_density()) 


#This is not working. Let's try something else
corpus_df_tidy %>% 
  anti_join(AllnonLEX_df, by = "word") %>% 
  count(word, sort = TRUE) #The most frequent lexical word is я - can be expected. Do I get rid of pronouns? Let me think

new_corpus2 <-corpus_df_tidy %>% 
  group_by(Student) %>% 
  summarize(total_words = n(),
         lexical_words = sum(!word %in% AllnonLEX_df$word),
         lexical_density = lexical_words/total_words)

new_corpus2 #Let's check at least one number from this result The result for text 1 is 6.203125 Why is is the wrong number. Let's check each output

corpus_df_tidy %>% 
  group_by(Student) %>% 
  summarize(nrow = nrow(lexical_words(corpus_df_tidy)))
```

```{r}
#Checking the output above. Let's upload one text
text1 <- readLines("C:/Users/Rossina/Documents/CMU_student/3_Fall_2021/Statistics_at_Pitt/2019_Standardized/2019_PreTest_ST/Pre_test_Prompt0_Planning_dinner_party_ST/Addison_Mitchell_Entry0_ST.txt", encoding = "UTF-8") %>% str_remove_all("unclear")
text1_df <- tibble(text = text1, Student = 1)
text1_df_tidy <- unnest_tokens(text1_df, word, text)
text1_df_tidy

# Lexical density
nrow(lexical_words(text1_df_tidy))/nrow(text1_df_tidy) #The result for text 1 is 0.796875 Why is it different?

lexical_words(text1_df_tidy) %>% nrow() #The answer is 51 lexical words
#what about all the words in the text?
nrow(text1_df_tidy) #The answer is 64 
51/64 #The result should be 0.79
```

